\documentclass{resume}

\usepackage{bookmark}
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry}

\name{Andrew Smith}
\address{+1(513) 240-8974 \\ 5844 Grazing Ct. Mason, OH}
\address{\href{mailto:smithdrew555@gmail.com}{smithdrew555@gmail.com} \\ \href{https://funplayer.xyz}{funplayer.xyz}}

\begin{document}

\begin{rSection}{Objective}
    {Software Engineer with 1 year of internship experience in Java, seeking Software Engineering Internship roles.}
\end{rSection}

\begin{rSection}{Education}
    \item {\bf Bachelor of Science in Computer Science \& Engineering}, The Ohio State University \hfill {Expected 2024}\\
    Relevant Coursework: Web Applications, Operating Systems, Algorithms and Data Structures.

    \item {\bf High School}, William Mason High School \hfill {2016 - 2020}\\
    Graduated with Honors (Summa Cum Laude)
\end{rSection}


\begin{rSection}{Skills}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{2em}} l }
        Programing languages & Rust, C, C++, x86-64 Assembly, WebAssembly, JS, Java, Ruby, Python, Matlab \\
        Tools                & Git, Github, Mercurial, Phabricator, Make, CMake, webpack                  \\
        UI Frameworks        & Java Swing, ReactJS, GatsbyJS, Ruby on Rails                               \\
    \end{tabular}
\end{rSection}

\begin{rSection}{Experience}
    \textbf{Software Engineering Internship} \hfill{May 2022 - Aug 2022}\\
    MIM Software \hfill \textit{Cleveland, OH}
    \begin{itemize}
        \itemsep -3pt {}
        \item Worked with a team to develop a desktop application using Java Swing
        \item Learned to work with a large codebase
        \item Developed a debugger to be used by the application's scripting program
    \end{itemize}
\end{rSection}

\begin{rSection}{Projects}
    \vspace{-1.25em}
    \item \textbf{LALR Parser/Interpreted language} Built a Look-Ahead Left-Right parser in C++ which makes heavy use of templates.
    Used the parser to make a simple scripting language with a C style syntax.
    (\href{https://funplayer.xyz/parser}{funplayer.xyz/parser})
    \item \textbf{Sudoku Solver} Built a sudoku puzzle solver in Rust using heuristics.
    (\href{https://funplayer.xyz/sudoku}{funplayer.xyz/sudoku})
    \item \textbf{Switch Controller} Built a program able to control a Nintendo Switch
    from a computer with the help of an Arduino Uno using C and C++.
    Additionally the program has the ability to capture and playback user input.
    The program also uses FFmpeg to capture video and audio data from the Nintendo Switch
    and do video and audio processing to automate actions.
\end{rSection}

\begin{rSection}{Extra-Curricular Activities}
    \begin{itemize}
        \item Participated in 2020 and 2021 Hack OHI/O hackathon
        \item Member of The Ohio State University Chess Club
        \item Member of an intramural soccer league
        \item Play the Viola and Piano
    \end{itemize}
\end{rSection}

\begin{rSection}{Leadership}
    \begin{itemize}
        \item Attended National Youth Leadership Training (NYLT)
        \item Attained the rank of Eagle Scout
    \end{itemize}
\end{rSection}

\end{document}
